Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex
made a few minor modifications
added walkthrough figure

\begin{figure}[t]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/smallEnv.pdf_tex}
\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.\label{fig:smallEnv}}
\end{figure}

@@

include algorithm block 2 from paper!  go with the one from the short version of the paper, since it's the version we're actually going with.  the algorithm block is shorter too

@@

\section{Benchmarking}

\begin{figure}[t]
\centering
\def\svgwidth{\textwidth}
\input{figures/benchmarks.pdf_tex}
\caption{Benchmarking Test Examples. The goal was to move the green block to another surface.\label{fig:benchmark}}

\end{figure}
\subsection{Testing}
We generated a set of small-scale tests to check the correctness of the interface layer. ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces. Some blocks were surrounded on 3 sides and others on all sides by walls and blocks. For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction. For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.

\subsection{Procedure}

>>>>

\begin{figure}[t]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/walkthrough.pdf_tex}
\caption{Walkthrough Example. The goal was for the red block to be on surface S.\label{fig:walkthrough}}
\end{figure}

@@

@@

\section{Benchmarking}
\subsection{Testing}
\begin{figure}[t]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/smallEnv.pdf_tex}
\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.\label{fig:smallEnv}}
\end{figure}
We generated a set of small-scale tests to check the correctness of the interface layer. ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces. Some blocks were surrounded on 3 sides and others on all sides by walls and blocks. For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction. For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.

\subsection{Procedure}
\begin{figure}[t]
\centering
\def\svgwidth{\textwidth}
\input{figures/benchmarks.pdf_tex}
\caption{Benchmarking Test Examples. The goal was to move the green block to another surface.\label{fig:benchmark}}

\end{figure}
